---
title: "Psych Data Science Lab @ BGU 2025 -Group GLAS"
author: "Gilad Sarusi, Lior Lipa, Adi Bitan and Sivan Hayek"
format:
  html:
    toc: true
    number-sections: true
    self-contained: true
    browse: true
execute:
  warning: false
  message: false
editor: visual
---

# The Objective

Can chains of spontaneous thought reveal mental health? In this competition, you'll work with rich psychological data to predict depression levels from free association patterns and demographic variables.

Using a dataset of participants who completed a depression questionnaire (CES-D) and a 10-round free association task, our goal is to predict each participant’s depression score using their unique trails of thought and background information.

For details about the challenge visit it's Kaggle page: [Depression Prediction Competitio](https://www.kaggle.com/competitions/depression-prediction/overview)n

# Feature Engineering

```{r}
library(tidyverse)
library(tidymodels)
library(quanteda)
library(embedplyr)
library(pdftools)
library(stringr)
library(text)
library(ggplot2)
library(readr)
library(patchwork)


training_set <- read.csv('./data/ds_train_full.csv')

# DO NOT TOUCH THIS ONE! 
test_set <- read.csv('./data/ds_test_full.csv')

# The prompt given to the subjects in each block:
prompts_given <- data.frame(
  prompt = c(
  "log",
  "orb",
  "extension",
  "synthesizer",
  "treadmill",
  "valet",
  "toss",
  "testimony",
  "mow",
  "forge"),
  order = 1:10
)




# Since each subject goes through 10 blocks that has 10 steps it means that our training set consists of 51800/100 subjects (518)

# Since that this is Goal oriented challenge where the justification of using one method instead of the other is relevant, we would use two method to split our traning set for validationL bootstrap (enable us to asses confidence) and Kfold CV (the standard and straightforward approach)

# NOTICE, the rows are not independent of one another- each subject has 100 rows so when splitting we need to ensure there's no data linkage. 

#Another consideration is class balance, we'll need to think whether or not we want strata sampling in bootstraps, meaning is there's any meaningful classes in training sets that might tilt the results towards one way due to unbalanced sampling in validation set vs the remaining set 

# ------ Pre-processing

#School need to be re arrange by order 
levels(factor(training_set$school))


# Income need to be re arrange by order 
levels(factor(training_set$Income))


hist(training_set$Age)
education_levels <- c(
  "Less than high school degree",
  "High school graduate (high school diploma or equivalent including GED)",
  "Some college but no degree",
  "Associate degree in college (2-year)",
  "Bachelor's degree in college (4-year)",
  "Master's degree",
  "Professional degree (JD, MD)",
  "Doctoral degree"
)
income_range_levels <- c(
  "Less than $10,000",
  "$10,000 to $19,999",
  "$20,000 to $29,999",
  "$30,000 to $39,999",
  "$40,000 to $49,999",
  "$50,000 to $59,999",
  "$60,000 to $69,999",
  "$70,000 to $79,999",
  "$80,000 to $89,999",
  "$90,000 to $99,999",
  "$100,000 to $149,999",
  "$150,000 or more"
)

# ----------- columns to remove to set ay subject level not observartion
vary_variables <-c("word",
                   "cycle",
                   "q_num",
                   "wordId")

#-------------------- Corpus, Embedding and Dictionaries ----------------

# Since   "docnames must be unique" we would create a word_id for every unique word
feature_engineering_funct <- function(dataset){
  
  
  training_corpus <- dataset |>
    mutate(word_id =row_number()) |>  
    corpus(docid_field = "word_id",
           text_field="word")
  
  
  # In order to use word_count methods we need that each participant's words (all 100 words) assign to him would be regarded as a text (let's say treatign his chains of words as one big 'tweet') then we would be able to count the the negative words in his chain
  
  training_corpus_per_subject <- dataset |>
    group_by(ID) |>
    summarise(words_all = paste(word, collapse = " "), .groups = "drop") |>
    ungroup() |>  
    corpus(docid_field = "ID",
           text_field="words_all") 
  
  
  
  # Tokenazation 
  
  #due to the nature of the task I don't see aby reason to stems or lemmas, the same goes for not using N-Gram - the task's output is one-word each step
  
  
  #Tokenazing the words with the current data structure might be useful later 
  
  training_tokens <- training_corpus |>
    tokens(  
      remove_punct = T,
      remove_symbols = T,
      remove_numbers = T) |>
    tokens_tolower()
  
  
  neg_sentiment_words <-read.table("data/NRC-Emotion-Lexicon-Wordlevel-v0.92.txt",
                                   header = TRUE, sep = "\t") |>
    mutate(word = aback,
           sentiment = factor(anger),
           associate= X0) |>
    select(-aback,-anger,-X0) |>
    filter(sentiment== "negative" & associate == "1")
  
  
  #------------------ Feature I - Negative Word Count -----------------  
  
  training_corpus_per_subject_token_dfm <- training_corpus_per_subject  |>
    tokens(  
      remove_punct = T,
      remove_symbols = T,
      remove_numbers = T) |>
    tokens_tolower() |>
    dfm()
  
  
  training_perS_neg_count <-training_corpus_per_subject_token_dfm |>
    dfm_lookup(
      dictionary(
        list(
          negative_count = neg_sentiment_words$word)
      )
    ) 
  
  # let's add it to our training set
  
  dataset <- dataset |>
    left_join(
      training_perS_neg_count |>
        convert("data.frame") |>
        rename(ID = doc_id) |>
        mutate(ID = as.numeric(ID)),
      by = "ID")
  
  #Sanity Check:
  
  table(dataset$negative_count)
  
  hist(dataset$negative_count)
  
  #VERY NICE (BORAT VOICING)!!! 
  
  
  # -------------- Feature II - Embedded CCR (CES-D) -----------------
  
  # The heavy lifting starts now! Let's enter the multidimentional vector world 
  
  # First I would fetch CES-D questioneare using 'stringr' and 'pdftools' packages:
  
  CES_D_items <- pdf_text("./data/epidemiologic-studies-scale.pdf") |>
    str_split("\\n(?=[0-9]+\\.)")  |>
    unlist() |>
    # keep only lines that start with number + dot
    str_subset("^[0-9]+\\.") |>
    # clean whitespace
    str_trim() |>
    # remove the leading number + dot + space, keep only the text
    str_remove("^[0-9]+\\.\\s*") |>
    tibble::tibble(item_number = 1:20,     
                   item_text   = _) |>
    
    # Dealing with reversed items 
    
    mutate(item_text = case_when(
      item_number == 4 ~ "I felt I was not as good as other people.",
      item_number == 8 ~ "I didn't felt hopeful about the future.",
      item_number == 12 ~ "I wasn't happy.",
      item_number == 16 ~ "I didn't enjoyed life.",
      
      #. Fixing Bad Parsing 
      item_number == 20 ~ "I could not get “going.",
      TRUE ~ item_text
    )) |>
    select(item_text) |>
    pull()
  
  sbert_embeddings <- function(texts) {
    textEmbed(
      texts,
      model = "sentence-transformers/all-MiniLM-L12-v2", 
      layers = -2,  # second to last layer (default)
      tokens_select = "[CLS]", # use only [CLS] token
      dim_name = FALSE,
      keep_token_embeddings = FALSE
    )$texts[[1]]
  } 
  
  
  #It makes more sense to pass the text of single words and not the combine per subject since
  # the contex are in effect when it comes to the word embedding of that word- since this is a free association task it should be forged into a non-sensed sentence.
  
  dataset <- dataset |>
    
    # every unique word gets an ID 
    mutate(wordId = dense_rank(word))
  
  
  
  # training_corpus_sbert <- dataset |>
  #   embed_docs(
  #     text_col = "word", 
  #     model = sbert_embeddings, 
  #     id_col = "wordId", 
  #     .keep_all = TRUE
  #     )
  #Save it as RDS to reduce computation time upon relaunch
  #     saveRDS(training_corpus_sbert,
  #        file = "./rds/training_corpus_sbert.rds")
  training_corpus_sbert <-readRDS("./rds/training_corpus_sbert.rds")
  
  
  depression_ccr <- CES_D_items |> 
    embed_docs(sbert_embeddings, output_embeddings = TRUE) |> 
    average_embedding()
  
  
  
  #getting the Cos Similiarity of each word to the CCR :
  
  WordId_depression_ccr <- training_corpus_sbert |>
    get_sims(
      Dim1:Dim384,
      list(depression = depression_ccr),
      method = "cosine_squished"
    )
  
  
  
  #Aggregating it to subject level not word level 
  
  
  subject_cos_sim <- WordId_depression_ccr |>
    group_by(ID) |>
    summarise(
      dep_cos_sim = mean(depression, na.rm = TRUE),
      dep_sim_sd  = sd(depression, na.rm = TRUE),
    ) |>
    ungroup()
  hist(subject_cos_sim$dep_cos_sim)
  
  
  # Adding it to our Training set :
  
  dataset <- dataset |> 
    left_join(subject_cos_sim,
              by ="ID")
  
  
  #---------------------- Feature III - DDR  -----------------------
  
  
  # Unlike CCR, where the items are sentences and the context of words affects their meaning, DDR follows a dictionary-based approach. Therefore, we would use word2vec for DDR embeddings, more suiting for static word embedding .
  
  #How many associations are word and how many are sentences ?
  
  n_multi <- sum(str_detect(dataset$word, "\\S\\s+\\S"), na.rm = TRUE)
  prop_multi <- mean(str_detect(dataset$word, "\\S\\s+\\S"), na.rm = TRUE)
  
  # less than 2% 
  
  
  
  #Since Word2Vec already uses static meaning of the words, use the per_subject df (in each all the 100 words are stacked in one string from each subject) for our embedding. Also, this aligns with the idea that every participant would get one DDR score 
  
  # options(download.file.method = "libcurl", timeout = 1200)
  # Sys.setenv(CURL_HTTP_VERSION = "1.1")
  #            
  # word2vec_model <- load_embeddings(
  #   model  = "cc.en.300",
  #   words  = featnames(training_corpus_per_subject_token_dfm),
  #   format = "rds",
  #   dir    = "./rds"
  # )


  
  word2vec_model<-readRDS("./rds/cc.en.300.rds")
  
  
  
  #Training the model on own corpus 
  word2vec_training_set <- training_corpus_per_subject_token_dfm |>
    textstat_embedding(word2vec_model)
  
  
  
  # Creating the DDR :
  
  negative_word2vec_ddr <- predict(word2vec_model,
                                   neg_sentiment_words$word) |> 
    average_embedding(w= "trillion_word", na.rm = T)
  
  # Warning: 2401 items in `newdata` are not present in the embeddings object.
  # the DDR is of 916 negative words 
  
  
  neg_mood_ddr_cossim <- word2vec_training_set |> 
    get_sims(
      dim_1:dim_300, 
      list(negative_DDR = negative_word2vec_ddr), 
      method = "cosine_squished"
    ) |>
    rename(ID= doc_id) |>
    mutate(ID = as.numeric(ID))
  
  
  
  #let's add that feature into our training set 
  
  dataset <- dataset |>
    left_join(neg_mood_ddr_cossim,
              by= "ID")
  
  
  
  
  # ------------ Feature IV - Semantic Distance (first Word)--------------
  
  # Several studies suggest that depression—especially rumination—is characterized by fixation on a narrow, predominantly negative semantic space. Consequently, I expect smaller semantic distances among associations in depressed participants.
  
  
  #Let's get the embedding of each word in the corpus, aka all the words subject use in the task. Firstly, we would embedd the prompted words: 
  
  E <- as.matrix(predict(word2vec_model, prompts_given$prompt))
  prompts_embedding <- data.frame(
    prompt_n = 1:nrow(E),
    word = rownames(E),
    E
  )
  for (q in 1:10) {
    # We are running on the first word given in each chain (cycle - where q_num == 1)
    # getting the prediction of the embedding by the model, adding the embedding to
    # the q1_words df. The q lop is needed because we compare the cos_sim to DIFFENERT word each cycle 
    
    q1_words <- dataset|>
      filter(q_num ==1) |>
      mutate(word = tolower(word))|> 
      select(word,
             wordId,
             cycle,
             q_num,
             ID)
    
    I1_emd <- as.matrix(predict(word2vec_model, unique(q1_words$word))) |>
      as.data.frame() |>
      rownames_to_column("word")
    
    # Adding the embedding to first words 
    q1_words <- q1_words |>
      left_join(I1_emd, by = "word") |>
      mutate(w2v_oov = if_else(!word %in% I1_emd$word, TRUE, FALSE))
    
    #Warning: 54 items in `newdata` are not present in the embedding object.
    
    
    d_prompt1_to_word1 <- q1_words  |> 
      get_sims(
        dim_1:dim_300, 
        list(d_0_1 = prompts_embedding |> 
               filter(prompt_n == q) |> 
               select(-word,-prompt_n) |>
               as.numeric()),
        method = "cosine_squished"
      )
  }
  
  # wide for each subject and add it to training set 
  dataset <- dataset |>
    left_join(d_prompt1_to_word1 |>
                pivot_wider(
                  id_cols = ID,
                  names_from = cycle,
                  names_glue = "d_0_1_c{cycle}",
                  values_from = d_0_1,
                  values_fill = NA_real_
                ),
              by ="ID") |>
    
    # creating a mean Distance from prompt to word 1  
    mutate(
      d_0_1_mean = rowMeans(pick(starts_with("d_0_1_c")), na.rm = TRUE)
    ) |>
  
  
  

  #Making that every Subject would have only one datapoint: 
  select(-vary_variables)|> 
  distinct(ID, .keep_all = TRUE)
  
  
   dataset
}


# Creating the features on the training set 

fe_training_set<- feature_engineering_funct(training_set)














```

# Visual representation of correlations

```{r}
#| label: Visual
#| message: false
#| warning: false



p1 <- ggplot(fe_training_set, aes(x = negative_count, y = matrixScore)) +
  geom_point(color = "#0072B2", size = 3, alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(
    x = "Negative Word Count", y = "matrixScore"
  ) +theme_minimal()


p2 <- ggplot(fe_training_set, aes(x = dep_cos_sim, y = matrixScore)) +
  geom_point(color = "#D55E00", size = 3, alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(
    x = "CCR", y ="matrixScore"
  )+theme_minimal()


p3 <- ggplot(fe_training_set, aes(x = negative_DDR, y = matrixScore)) +
  geom_point(color = "#009E73", size = 3, alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(
    x = "DDR)", y = "matrixScore"
  )+theme_minimal()


p4 <- ggplot(fe_training_set, aes(x = d_0_1_mean, y = matrixScore)) +
     geom_point(color = "#CC79A7", size = 3, alpha = 0.6) +
     geom_smooth(method = "lm", se = TRUE) +
     labs(
       x = "Semantic Distance", y = "matrixScore"
     )+theme_minimal()
  
combined <- (p1 | p2) / (p3 | p4) +
  plot_annotation(
    title = "Correlations between Depression Level and Four Depression-Related Measures",
    subtitle = "Each panel shows a linear fit and SE",
    theme = theme(
      plot.title = element_text(size = 16, face = "bold"),
      plot.subtitle = element_text(size = 12),
      plot_annotation(
        caption = "Depression Level (matrixScore)"
      )
    )
  )

combined

```

# Modeling

## Random Forest

```{r}
set.seed(130597)



fe_training_set<- feature_engineering_funct(training_set)




splits <- initial_split(fe_training_set,
                        prop = 0.7,
                        strata = matrixScore)
training_07 <- training(splits)
test_03 <- testing(splits)



# Bootstraps Spliting
validation_sets <- bootstraps(
  training_07,
  times = 50,
  strata = matrixScore,
  apparent = F
)

comparison_sets <- bootstraps(
  test_03,
  times = 50,
  strata = matrixScore,
  apparent = F
)

#the predictions would be evaluated using R2 and MAE

mset_reg <- metric_set(rsq, rmse)



#--------------- Recipe ---------------------



rec <- recipe(matrixScore ~ ., data = training_07) |>
  step_rename(
    school_text = school,
    Income_text = Income
  ) |>
  step_mutate(
    
    
    #Setting the leveled vector  for school 
    school_text = factor(school_text,
                         levels = education_levels,
                         ordered = TRUE),
    # Creating an ordered school numeric column
    school_level = as.integer(school_text),
    
    #------- Factoring the needed columns -------,
    race = factor(coalesce(race_1,race_2,race_3,race_4,race_5,race_6)),
    
    #since non-white together only serves less than 15% of the data I would create a white column insterad of race indicating that the subject is white or not 
    race = ifelse(race != "White", 0,1),
    
    #theres only only 'rather not say' sex type so leaving it Male.. 
    # this is more od a bandaid than a theoretical consideration  
    sex = case_when(
      sex == "Rather not say" ~ 1,
      sex == "Male" ~ 1,
      sex == "Female" ~ 0),
    sex = factor(sex),
    race = factor(race),


    # ----------- Giving numeric value to income ---------
    
      income_units = case_when(
      Income_text == "Less than $10,000"  ~ 5000,
      Income_text == "$10,000 to $19,999"     ~ 15000,
      Income_text == "$20,000 to $29,999"     ~ 25000,
      Income_text == "$30,000 to $39,999"     ~ 35000,
      Income_text == "$40,000 to $49,999"     ~ 45000,
      Income_text == "$50,000 to $59,999"     ~ 55000,
      Income_text == "$60,000 to $69,999"     ~ 65000,
      Income_text == "$70,000 to $79,999"     ~ 75000,
      Income_text == "$80,000 to $89,999"     ~ 85000,
      Income_text == "$90,000 to $99,999"     ~ 95000,
      Income_text == "$100,000 to $149,999"   ~ 125000,
      Income_text == "$150,000 or more"       ~ 175000,
      )) |>
        
 
  # Change race to white for easier unsersatnding
  step_rename(
    White = race
  ) |>
  
  #-------- Remove features ----------
  step_rm(
    Income_text,
    school_text,
    race_1,
    race_2,
    race_3,
    race_4,
    race_5,
    race_6,
    race_6_TEXT,
    ID, 
    # Leaving just the mean distance betwen the first and the second word
    starts_with("d_0_1_c")
  ) |>

  
  
  # -------- Dealing with NA ----------

  # I'll use KNN imputation so normalization is needed 
  step_normalize(all_numeric_predictors(), id = "norm") |>
  step_impute_knn(all_predictors(), neighbors = 5) |>
  
  #   # I'll keep in mind that in order for me to interpratate it  because normalization doesn't needed Rnd frst and boosting are not effect by normalization It probably won't hurt but still
  
  
  # drop zero-variance columns
  step_zv(all_predictors())


  

# See if the steps done correctly 
tasting <- bake(prep(rec, training_set = training_07), NULL)

view(tasting)

# -------------------------  Random Forest ------------------

rf_spec <- rand_forest(
  mode = "regression",
  engine = "randomForest",
  
  #we will tune these hyper-parameters
  
  mtry = tune(),
  trees = tune(),
  min_n = 5
)

rf_wf <- workflow(preprocessor = rec, spec = rf_spec)


rf_grid <-  grid_regular(
  
  #Considering to computation time I would reduce the max number of predictors to 10 
  mtry(range = c(1, 10)),
  trees(range = c(100, 500)),
  levels = 5
)

### --------- Tuner ---------
 # rf_tuner <- tune_grid(rf_wf,
 #                      resamples = validation_sets,
 #                      grid = rf_grid,
 #                     metrics = mset_reg)

# saveRDS(rf_tuner, file = "./rds/rf_tuner.rds")

rf_tuner <-  readRDS("./rds/rf_tuner.rds")


# --------- Scheming an ploting 



autoplot(rf_tuner)


# when it comes to rmse it seems that the more the merrier hwever the picture is not that clear in rsq , carying greatly and non linearly as a function of number of trees, given that the margins in rmse aren't that big the criterion would be rsq

# Wild guess:  my horse is 175 trees and 3 predictors!


## ---- Trees -----
#Best - one SD

best_oneSD_trees<- select_by_one_std_err(rf_tuner,
                                      trees,
                                      metric = "rsq")
# tree= 100
#mtry= 1 


# ------- number of predictors in each Tree --------

best_oneSD_mtry<- select_by_one_std_err(rf_tuner,
                                      mtry,
                                      metric = "rsq")
# Again: 
# tree= 100
#mtry= 1 

# ------ Best overall --------
best_ovrll<- select_best(rf_tuner,
                               metric = "rsq")
# tree= 175
#mtry= 3


# Note to Self- Always check the Y-axis scale before interpreting visual differences. What appears to be a large gap between options might actually be insignificant. 

# In this case since every point counts and we hope to scrach the 0.3 bench mark I would go with mtry=3 and tree=175


# Therefore, the selected hyperparameters are:
#tree = 175
#mtry = 3




##------- Training and Fitting -------

rf_fit <- rf_wf |>
  finalize_workflow(parameters = best_ovrll) |> 
  fit(data = training_07)
rf_fit 

rf_fit_simpler <- rf_wf |>
  finalize_workflow(parameters = best_oneSD_mtry) |> 
  fit(data = training_07)

rf_pred <- predict(rf_fit, new_data = training_07) |> 
  bind_cols(training_07)

rf_pred_simpler <- predict(rf_fit_simpler, new_data = training_07) |> 
  bind_cols(training_07)

mae(rf_pred, truth = matrixScore, estimate = .pred )
#1 mae     standard         4.80



rsq(rf_pred, truth = matrixScore, estimate = .pred )
# 1 rsq     standard       0.95

cor(rf_pred$matrixScore,
    rf_pred$.pred,
    method= "pearson" )

# Performance on TRAINING SET: 
          # MAE:  4.80
          # R2: 0.95
          # r: 0.92
## ----- Testing the test set -------

test_pred_rnd <- augment(rf_fit, test_03)

test_pred_rnd |> 
  mset_reg(matrixScore, .pred)

  cor(test_pred_rnd$.pred,
      test_pred_rnd$matrixScore,
      method = "pearson")
  
  
test_pred_rnd_simpler <- augment(rf_fit_simpler,
                         test_03)

test_pred_rnd |> 
  mset_reg(matrixScore, .pred)


cor(test_pred_rnd$.pred,
      test_pred_rnd$matrixScore,
      method = "pearson")
mae(test_pred_rnd, truth = matrixScore, estimate = .pred )
rsq(test_pred_rnd, truth = matrixScore, estimate = .pred )

  
  
# Performance on TEST SET: 
          # MAE:  10.4
          # R2: 0.04
          # r: 0.21


## ------The  Bootstrap Test --------

# This would be serve later on to compare between the two models
rf_test_comp <- rf_wf |> 
  finalize_workflow(parameters = best_ovrll)|>
    fit_resamples(resamples = comparison_sets,
                  metrics = mset_reg)

            

```

## Booster

```{r}


boost_spec <- boost_tree(
  mode = "regression",
  engine = "xgboost",
  
  ## Complexity
  tree_depth = 2, # [1, Inf] limits the depth of each tree
  min_n = 5, # [1, Inf] don't split if you get less obs in a node
  
  
  loss_reduction = 0, # [0, Inf] node splitting regularization - no need for regulation since I will keep tree depth at 1 
  
  ## Gradient
  learn_rate = 0.1, # [0, 1] learning rate
  trees = tune(),
  
  ## Randomness
  mtry = 3,  # to help me comparing with Random Forest model and since it is close to the theoretical recommendation when it come to regression sqrt(p)
  sample_size = tune() # [0, 1] proportion of random data to use in each tree
)

booster_wf <- workflow(preprocessor = rec |> 
                         
                         #Booster doens't know how to deal with nominal and 
                         #factors so: 
                           step_dummy(all_nominal_predictors(),
                                      one_hot = TRUE),
                       spec = boost_spec)

booester_grid <-  expand_grid(
  trees= seq(100, 1000, by = 100),
  sample_size =  seq(0.1, 1, by = 0.1),
  )

 booster_tuner <- tune_grid(booster_wf,
                       resamples = validation_sets,
                       grid = booester_grid,
                       metrics = mset_reg)
 saveRDS(booster_tuner,"./rds/booster_tuner")
 booster_tuner<- readRDS("./rds/booster_tuner")
 
 
one_SD_smplsz_boost <-select_by_one_std_err(booster_tuner,
                                      sample_size,
                                      metric ="rsq")
one_SD_tress_boost <- select_by_one_std_err(booster_tuner,
                      trees,
                      metric ="rsq")

best_ovrll_boost <- select_best(booster_tuner,
                      metric ="rsq")

# All is evidant that the best is sample_size=0.1, tree=100

##------- Training and Fitting -------

boost_fit <- booster_wf |>
  finalize_workflow(parameters = best_ovrll_boost) |> 
  fit(data = training_07)
boost_fit 

boost_pred<- predict(boost_fit, training_07) |> 
  bind_cols(training_07)

 mae(boost_pred,
     truth =matrixScore ,
     estimate = .pred)
 rsq(boost_pred,
     truth =matrixScore ,
     estimate = .pred)
  cor(boost_pred$.pred,
      boost_pred$matrixScore,
      method="pearson")
 

# Performance on TRAINING SET: 

# MAE:   9.48
# R2: 0.24
# r: 0.49  
 
## ----- Testing the test set -------

test_pred_boost <- augment(boost_fit,
                           test_03)

 mae(test_pred_boost,
     truth =matrixScore ,
     estimate = .pred)
 rsq(test_pred_boost,
     truth =matrixScore ,
     estimate = .pred)
  cor(test_pred_boost$.pred,
      test_pred_boost$matrixScore,
      method="pearson")
  


# Performance on TEST SET: 

# MAE:   10.1
# R2: 0.08
# r: 0.28

## ------The  Bootstrap Test --------

# This would be serve later on to compare between the two models
boost_test_comp <- booster_wf |> 
  finalize_workflow(parameters = best_ovrll_boost)|>
    fit_resamples(resamples = comparison_sets,
                  metrics = mset_reg)
  
  


```

# Comparison

```{r}

library(knitr)

Booster_rnds_metrics_com <- bind_rows(
  "rf" = collect_metrics(rf_test_comp, summarize = FALSE),
  "boosting" = collect_metrics(boost_test_comp, summarize = FALSE),
  
  .id = "Model"
) |>
  mutate(
    Model = factor(Model, levels = c("rf", "boosting"))
  )


Booster_rnds_metrics_com |>
  group_by(id, .metric) |>
  mutate(
    best_model = case_match(.metric,
                            "rmse" ~ Model[which.min(.estimate)],
                            "rsq" ~ Model[which.max(.estimate)])
  ) |>
  ggplot(aes(Model, .estimate, color = Model)) +
  facet_wrap(facets = vars(.metric), scales = "free") +
  stat_summary(size = 1, 
               position = position_nudge(0.1), 
               show.legend = FALSE) + 
  geom_point() +
  geom_line(aes(group = id, color = best_model))


```

# OOS Predictions

```{r}

# Creating the predictions for the real TEST!


#adding the features: 

fe_training_set<- feature_engineering_funct(training_set)
fe_test_set <- feature_engineering_funct(test_set|> mutate(race_5 = NA))


# -------- Random Forest ----------

#Train on full training set
final_fit_rf <-  rf_wf |>
  finalize_workflow(parameters = best_ovrll) |> 
  fit(data = fe_training_set)
final_fit_rf 


REAL_test_pred_rnd <- augment(final_fit_rf, fe_test_set) |>
  select(ID,.pred) |>
  rename(matrixScore = .pred) |>
  arrange(ID)

# -------- Boosting ----------
final_boost_fit <-  booster_wf |>
  finalize_workflow(parameters = best_ovrll_boost) |> 
  fit(data = fe_training_set)
final_boost_fit 



REAL_test_pred_boost <- augment(final_boost_fit, fe_test_set)|>
  select(ID,.pred) |>
  rename(matrixScore = .pred) |>
  arrange(ID)


# Write prediction files with correct header
write_csv(REAL_test_pred_rnd, "./predictions/predictions_random_forest.csv")
write_csv(REAL_test_pred_boost, "./predictions/predictions_boost.csv")

```
